### 2013-12-17 poster/poster.tex
minor changes

\textbf{Pros} 
Reduce replication overhead; Eliminate network inconsistency; Enable smooth transition across management barriers \\ \\
\textbf{Price we pay}  \\
Sub-optimality for inter-domain operations. How much is the deviation from optimality ?

@@

 %----------------------------------------------------------------------------------------
%	REFERENCES
%----------------------------------------------------------------------------------------
\color{SaddleBrown}
\section*{RESOURCES}
\color{DarkSlateGray}
https://github.com/MugiwaraLuffy/ACN/ \\
https://github.com/SWIMProjectUCB/SWIM
\nocite{*} % Print all references regardless of whether they were cited in the poster or not
%\bibliographystyle{plain} % Plain referencing style
\bibliography{sample} % Use the example bibliography file sample.bib

>>>>

\textbf{Pros}
\begin{itemize}
    \item Reduces replication overhead
    \item Minimizes network inconsistency
    \item Enables smooth transition across management barriers
\end{itemize}
\textbf{Price we pay}  \\
Sub-optimality for inter-domain operations. How much is the deviation from optimality ?

@@

 %----------------------------------------------------------------------------------------
%	REFERENCES
%----------------------------------------------------------------------------------------
\color{SaddleBrown}
\section*{RESOURCES}
\color{DarkSlateGray}
https://github.com/MugiwaraLuffy/ACN/ \\
https://github.com/SWIMProjectUCB/SWIM
%\nocite{*} % Print all references regardless of whether they were cited in the poster or not
%\bibliographystyle{plain} % Plain referencing style
%\bibliography{sample} % Use the example bibliography file sample.bib
